Topic modeling bla bla

### 2017-05-30 thesis_report/draft_thesis.tex
Minor fixes in formating

\begin{enumerate}
  \item Fix a multinomial distribution with parameter vector $\phi$ of length $V$
  \item for each word in the document:
  \begin{itemize}
  draw a word $w$ according to $\phi$
  \end{itemize}
\end{enumerate}

@@

\begin{enumerate}
\item Fix a multinomial $\alpha$ over categories $1$ to $K$\\
for category number $1$ to category number $K$:
\begin{itemize}
fix a multinomial with parameter vector $\phi_k$
\end{itemize}

\item for document number $1$ to document number $M$:
\begin{itemize}
draw a category $z$ according to $\alpha$\\
for each word in the document:\\
  	\begin{itemize}
  		draw a word $w$ according to $\phi_z$
  	\end{itemize}
\end{itemize}
\end{enumerate}
\vspace{3mm}

@@

\begin{enumerate}
\item Pick a document $w$ with probability $p(w)$
\item For each of the $N$ words in $w$:
\begin{itemize}
(a) Pick a topic $z$ with probability $p(z|w)$
\end{itemize}
\begin{itemize}
(b) Generate a word $w$ with probability $p(w|z)$
\end{itemize}
\end{enumerate}

@@

\begin{enumerate}
\item Randomly choose a distribution over topics.
\item For each word in the document:
\begin{itemize}
(a) Randomly choose a topic from the distribution over topics in step #1.
\end{itemize}
\begin{itemize}
(b) Randomly choose a word from the corresponding distribution over the vocabulary.
\end{itemize}
\end{enumerate}

@@

This statistical model reflects the intuition that documents exhibit multiple topics. Each document exhibits the topics with different proportion (step #1); each word in each document is drawn from one of the topics (step #2b), where the selected topic is chosen from the per-document distribution over topics (step #2a). All the documents in the corpus share the same set of topics, but each document exhibits those topics with different proportion - that’s the distinguishing characteristic of LDA.
A more detailed explanation of the model follows in section 2.x.x.\par

>>>>

\begin{enumerate}
  \item Fix a multinomial distribution with parameter vector $\phi$ of length $V$
  \item for each word in the document:
  \begin{description}
  \item draw a word $w$ according to $\phi$
  \end{description}
\end{enumerate}

@@

\begin{enumerate}
\item Fix a multinomial $\alpha$ over categories $1$ to $K$\\
for category number $1$ to category number $K$:
\begin{description}
\item   fix a multinomial with parameter vector $\phi_k$
\end{description}

\item for document number $1$ to document number $M$:
\begin{description}
\item draw a category $z$ according to $\alpha$
\item for each word in the document:
  	\begin{description}
  	\item	draw a word $w$ according to $\phi_z$
  	\end{description}
\end{description}
\end{enumerate}
\vspace{3mm}

@@

\begin{enumerate}
\item Pick a document $w$ with probability $p(w)$
\item For each of the $N$ words in $w$:
\begin{description}
\item (a) Pick a topic $z$ with probability $p(z|w)$
\end{description}
\begin{description}
\item (b) Generate a word $w$ with probability $p(w|z)$
\end{description}
\end{enumerate}

@@

\begin{enumerate}
\item Randomly choose a distribution over topics.
\item For each word in the document:
\begin{description}
	\item (a) Randomly choose a topic from the distribution over topics in step 1.
\end{description}
\begin{description}
	\item (b) Randomly choose a word from the corresponding distribution over the vocabulary.
\end{description}
\end{enumerate}

@@

This statistical model reflects the intuition that documents exhibit multiple topics. Each document exhibits the topics with different proportion (step 1); each word in each document is drawn from one of the topics (step 2b), where the selected topic is chosen from the per-document distribution over topics (step 2a). All the documents in the corpus share the same set of topics, but each document exhibits those topics with different proportion - that’s the distinguishing characteristic of LDA.
A more detailed explanation of the model follows in section 2.x.x.\par
